---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fantasypl - An R Package for Fantasy Premier League Data

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/fantasypl)](https://CRAN.R-project.org/package=fantasypl)
[![Codecov test coverage](https://codecov.io/gh/danieloc1989/fantasypl/branch/master/graph/badge.svg)](https://app.codecov.io/gh/danieloc1989/fantasypl?branch=master)
[![R-CMD-check](https://github.com/danieloc1989/fantasypl/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/danieloc1989/fantasypl/actions/workflows/R-CMD-check.yaml)
<!-- badges: end -->

The goal of `{fantasypl}` is to retrieve data from the Fantasy Premier League API endpoints and provide it in a convenient tabular format (tibble).

## Installation

You can install the development version of `{fantasypl}` from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("danieloc1989/fantasypl")
```
There is no intention of releasing this package on CRAN.

## Retrieving FPL data

```{r}
library(fantasypl)
```

The package provides functions to retrieve various types of FPL data, including player information, team details, gameweek information, and more.


### Player Information

You can obtain general player information for all `r nrow(fpl_player_info())` registered players in the Premier League:

```{r player-general}
# General details of all players
fpl_player_info()
```

This function returns basic information such as names, teams, positions, and player IDs.

For more all player season statistics, you can use:

```{r player-season-stats}
# Season statistics of all players 
fpl_player_stats()
```

If more detailed level of information is required

```{r}
# Find player's ID
haaland <- fpl_find_player_id("haaland")

# Retrieve Haaland season statistics
fpl_player_fixture_stats(haaland)
```

### Team Information

To get information about all Premier League teams, you can use:

```{r pl-teams}
# PL team info
fpl_team_info()
```

*Team information has not been updated as of yet on the system. A warning will be introduced to this function if this persists.*

### Gameweek and Fixtures Information

To obtain information about gameweeks and fixtures, you can use the following functions:

```{r gameweek}
# Information on gameweeks
fpl_gameweek_info()

# Each PL fixture
fpl_fixtures_info()
```


### Weekly Dream Team

You can retrieve the Dream Team for the current gameweek like this:

```{r dreamteam}
# The Dream Team for the current gameweek
fpl_dreamteam()
```


## Additional Notes

The API may be unavailable for a brief period after a gameweek deadline as the system updates manager selections.

## Contributing

If you find issues or have suggestions for improvements, please open an issue on the [GitHub repository](https://github.com/danieloc1989/fantasypl/issues). I welcome contributions and collaboration.

## License
This package is released under the MIT License.

Happy fantasy gaming with `{fantasypl}`!
