---
title: "Introduction to {fantasypl}"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to {fantasypl}}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r options, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The {fantasypl} package is an R package that provides a convenient way to interact with the Fantasy Premier League API endpoints. It leverages the [{httr2}](https://httr2.r-lib.org/) package for making HTTP requests and integrates seamlessly with tidyverse packages for data manipulation and analysis.

## Installation

You can install the development version of the {fantasypl} package using the {pak} package:

```{r install, eval=FALSE}
# install.packages("pak")
pak::pak("danieloc1989/fantasypl")
```

As of this time, there is no intention of releasing the package on CRAN.

## Overview

The package offers functions to retrieve various types of information from the Fantasy Premier League API endpoints, such as team data, player statistics, fixtures, and more.

```{r setup}
library(fantasypl)
```

## Data Formatting

The data retrieved from the API endpoints are often not in a convenient tabular format. For instance, the 'bootstrap-static' endpoint (general information in FPL) returns a list with a mix of dataframes, lists, and other objects:

```{r}
# API URL
fpl_url <- "https://fantasy.premierleague.com/api"
 
# Retrieving bootstrap-static endpoint data
general_info <-
  httr2::request(fpl_url) |> 
  httr2::req_url_path_append("bootstrap-static") |> 
  httr2::req_perform() |> 
  httr2::resp_body_string() |> 
  jsonlite::fromJSON()

# First level structure of the bootstrap-static endpoint output
str(general_info, max.level = 1)
```

To improve the usability of the data, the {fantasypl} package reformats and organises the data into logical tabular structures.

### Example: Team Data

One example is the team data obtained from the 'teams' dataframe in the 'bootstrap-static' endpoint. By default, the ordering of the columns in the raw data does not make sense:

```{r}
# Original ordering of columns in teams dataframe
general_info$teams |> 
  str()
```

The {fantasypl} package renames some of the columns and reorganises the data for better readability:

```{r}
# Improved naming and ordering of columns in teams dataframe
fpl_team_info() |> 
  str()
```
